A decomposition Approach for solving the JSP using multi-shot ASP\thanks{Supported by organization x.}

### 2022-04-13 ICLP Paper/samplepaper.tex
small change

While decision versions of scheduling problems can be successfully modeled and
solved by an extension of ASP with Difference Logic (DL) constraints
\citep{gebser2016theory}, implemented by \clingodl on top of the
(multi-shot) ASP system \clingo \citep{gekakasc17a},
the optimization capacities of \clingodl come to their limits on moderately sized
yet highly combinatorial JSP instances \citep{elkgeb20a}, for some of which optimal solutions are so far unknown \citep{shysha18a}.
Successful application areas beyond JSP include 
industrial printing \citep{balduccini11a},
team-building \citep{rigralmaliiile12a},
shift design \citep{abseher2016shift},
course timetabling \citep{bainkaokscsotawa18a},
lab resource allocation \citep{francescutto2021solving},
and
medical treatment planning \citep{dogagrmamopo21a},
pointing out the general attractiveness of ASP for modeling and solving scheduling problems.

@@

\section{Conclusions}\label{sec:conclusions}
%
Our work develops multi-shot ASP modulo DL methods for JSP solving,
based on problem decomposition into balanced time windows that respect the operation
precedence within jobs and successive makespan optimization while extending
partial schedules to a global solution.
We demonstrate that splitting highly complex JSP instances into
balanced portions, for which partial schedules of good quality can be reliably
found within tight runtime limits, leads to significantly better global solutions
than obtainable with single-shot ASP modulo DL optimization in similar runtime.
Related works taking advantage of single- \citep{abjoossctowa21a}
and multi-shot solving \citep{francescutto2021solving} by
\clingodl to tackle real-world scheduling problems evaluate threshold values
on DL variables and perform optimization by means of common 
\lstinline{#minimize} statements of \clingo rather than minimizing the
value of a DL variable like \lstinline{makespan} in Listing~\ref{prg:encoding}.
Applying a similar approach can be advantageous in our future work as it may
potentially improve computational efficiency as well as solution quality further
and is even a necessity to switch from the makespan as optimization objective to tardiness
w.r.t.\ deadlines, which are crucial in many application areas.
While Machine-based decomposition turned out to be helpful
for finding better schedules, the strategies presented in Section~\ref{subsec:decomposition}
can be regarded as naive heuristics based on straightforward instance properties,
and incorporating machine-learning approaches \citep{elscge22a,tagesc21a}
for more adept partitioning is another promising direction for future work.
\hl{Provided the adjustment of problem decomposition strategies, 
our multi-shot solving methods can also be applied to the 
Flow-shop and Open-shop Scheduling Problems} \citep{taillard1993benchmarks}.
% \hl{Furthermore, it would be beneficial to apply the same approach to Flow-shop and open-shop scheduling problems. However, the proposed model must be changed to solve open-shop since the precedence constraint is not applied}
Moreover, we aim to generalize our methods further, e.g.,
by considering flexible machine allocations and varying processing times,
and scale them up to large real-world scheduling problems with an order of magnitude more
operations than in synthetic benchmarks.
%
% In this work, different decomposition strategies have been proposed for solving the Job-shop Scheduling Problem (JSP) using a multi-shot Answer Set Programming with Difference Logic constraints to handle the decomposition approach and the problem constraints. The proposed model split the problem into sub-problems using different decomposition strategies and then optimized each separately while minimizing the Makespan. The proposed model has been developed to improve the performance by applying the overlap between TWs to fix the decomposition mistakes. In addition, the compression of each window is to fulfill the gaps that occurred during the optimization process. We tested our model on a set of benchmark instances and the experiments have shown that i) considering the bottleneck machines during the decomposition process is effective, ii) The overlap between TWs improves the solution quality, and iii) the compression of TWs is super practical, as it aided the proposed model to obtain better solutions in less computational time. Our work can be extended by linking the optimization model with a simulator that considers more realistic factors such as machine breakdowns, new job arrivals and order cancellations.

>>>>

While decision versions of scheduling problems can be successfully modeled and
solved by an extension of ASP with Difference Logic (DL) constraints
\citep{gebser2016theory}, implemented by \clingodl on top of the
(multi-shot) ASP system \clingo \citep{gekakasc17a},
the optimization capacities of \clingodl come to their limits on moderately sized
yet highly combinatorial JSP instances \citep{elkgeb20a}, for some of which optimal solutions are so far unknown \citep{shysha18a}.
Successful \hl{applications in} areas beyond JSP include 
industrial printing \citep{balduccini11a},
team-building \citep{rigralmaliiile12a},
shift design \citep{abseher2016shift},
course timetabling \citep{bainkaokscsotawa18a},
lab resource allocation \citep{francescutto2021solving},
and
medical treatment planning \citep{dogagrmamopo21a},
pointing out the general attractiveness of ASP for modeling and solving scheduling problems.

@@

\section{Conclusions}\label{sec:conclusions}
%
Our work develops multi-shot ASP modulo DL methods for JSP solving,
based on problem decomposition into balanced time windows that respect the operation
precedence within jobs and successive makespan optimization while extending
partial schedules to a global solution.
We demonstrate that splitting highly complex JSP instances into
balanced portions, for which partial schedules of good quality can be reliably
found within tight runtime limits, leads to significantly better global solutions
than obtainable with single-shot ASP modulo DL optimization in similar runtime.
Related works taking advantage of single- \citep{abjoossctowa21a}
and multi-shot solving \citep{francescutto2021solving} by
\clingodl to tackle real-world scheduling problems evaluate threshold values
on DL variables and perform optimization by means of common 
\lstinline{#minimize} statements of \clingo rather than minimizing the
value of a DL variable like \lstinline{makespan} in Listing~\ref{prg:encoding}.
Applying a similar approach can be advantageous in our future work as it may
potentially improve computational efficiency as well as solution quality further
and is even a necessity to switch from the makespan as optimization objective to tardiness
w.r.t.\ deadlines, which are crucial in many application areas.
\hl{While Machine-based decomposition turned out to be helpful
for finding better schedules, the strategies presented in Section}~\ref{subsec:decomposition}
\hl{can be regarded as naive heuristics based on straightforward instance properties,
and incorporating machine-learning approaches} \citep{elscge22a,tagesc21a}
\hl{for more adept partitioning is another promising direction for future work.
Provided the adjustment of problem decomposition strategies, 
our multi-shot solving methods can also be applied to the 
Flow-shop and Open-shop Scheduling Problems} \citep{taillard1993benchmarks}.
% \hl{Furthermore, it would be beneficial to apply the same approach to Flow-shop and open-shop scheduling problems. However, the proposed model must be changed to solve open-shop since the precedence constraint is not applied}
Moreover, we aim to generalize our methods further, e.g.,
by considering flexible machine allocations and varying processing times,
and scale them up to large real-world scheduling problems with an order of magnitude more
operations than in synthetic benchmarks.
%
% In this work, different decomposition strategies have been proposed for solving the Job-shop Scheduling Problem (JSP) using a multi-shot Answer Set Programming with Difference Logic constraints to handle the decomposition approach and the problem constraints. The proposed model split the problem into sub-problems using different decomposition strategies and then optimized each separately while minimizing the Makespan. The proposed model has been developed to improve the performance by applying the overlap between TWs to fix the decomposition mistakes. In addition, the compression of each window is to fulfill the gaps that occurred during the optimization process. We tested our model on a set of benchmark instances and the experiments have shown that i) considering the bottleneck machines during the decomposition process is effective, ii) The overlap between TWs improves the solution quality, and iii) the compression of TWs is super practical, as it aided the proposed model to obtain better solutions in less computational time. Our work can be extended by linking the optimization model with a simulator that considers more realistic factors such as machine breakdowns, new job arrivals and order cancellations.
